% Cover letter / response to reviewers — OARF
% Compile with pdflatex (OT1 text encoding -> vector Computer Modern Type-1 fonts).
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{cmap}
\input{glyphtounicode}
\pdfgentounicode=1
\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{xurl}
\usepackage{parskip}

\newcommand{\reviewer}[1]{\medskip\noindent\textbf{#1}\par}
\newcommand{\response}{\noindent\emph{Response.}\ }

\begin{document}

\thispagestyle{empty}

\noindent
The Editors\\
\textit{Computational Economics}\\
Springer

\bigskip
\noindent Re: Revised submission --- \textbf{``Online Anchor-Robust Forecasting under
Economic Regime Shift''}

\bigskip
\noindent Dear Editors,

Thank you for the opportunity to submit a revised version of our manuscript, and please
convey our thanks to the reviewer for an exceptionally constructive sequence of reports.
The successive reviews have materially improved the paper: they pushed us from an
over-claimed framing toward an honest, carefully scoped contribution, and they prompted
two new experiments that we believe close the last substantive gaps.

We summarise the paper's positioning, then respond point by point to the most recent
report. All changes are in the resubmitted manuscript; line and section references
below are to that version.

\section*{Summary of the contribution}

We present \textsc{OARF}, an online (streaming, leak-free) implementation of anchor
regression for forecasting under economic regime shift, together with an
interventional-robustness evaluation protocol and a diagnostic empirical study. We are
deliberate about scope:
\begin{itemize}[leftmargin=1.4em,itemsep=1pt]
\item The \emph{fixed-channel} method is the core contribution. It carries a
fixed-anchor interventional-regret guarantee (two rates, $O(\sqrt{T(1{+}K)})$ with
oracle moments and $O((1{+}K)T^{2/3})$ with online EMA moments) and, on a controlled
SCM with a held-out intervention grid, cuts worst-case interventional error well below
reactive and distributionally robust online learners.
\item The \emph{learned-channel} add-on (\textsc{OARF-CD}) is presented as exploratory
and diagnostic only: it is heuristic, unstable across seeds, and not covered by the
theorem.
\item On sixteen years of public daily energy variance-proxy data the method is
competitive but \emph{not} statistically superior --- every retained method lies in the
Model Confidence Set --- and we report this null result plainly.
\end{itemize}
The paper is thus a methodological and diagnostic contribution: a streaming
anchor-regression update, an interventional-robustness protocol, and stress tests and
scenarios mapping when proactive anchor robustness helps and when it fails.

\section*{Point-by-point response to the latest report}

\reviewer{1. Keyword ``causal robustness'' may invite stricter causal-identification
expectations.}
\response We replaced it with ``anchor robustness; interventional robustness'' and use
``anchor-based interventional robustness'' consistently in the text.

\reviewer{2. Related work still says OARF ``learns the anchor channel from data.''}
\response Revised to: ``\dots makes the estimator online; we additionally study a
heuristic add-on that attempts to estimate the anchor channel from data, while treating
the analyst-supplied channel as the primary mode.''

\reviewer{3. ``OARF aims to make the trigger unnecessary'' is too strong.}
\response Softened to: ``\dots tests whether, when an informative anchor is available,
part of the need for reactive triggering can be reduced \dots''

\reviewer{4. ``Never dominated'' reads as a formal Pareto claim.}
\response We removed dominance language. The real-data statement now reads: ``OARF is
statistically indistinguishable from the strongest baselines and broadly competitive
across metrics, but the public daily data do not provide statistically decisive
evidence of superior performance for any method, OARF included.''

\reviewer{5. The contribution may now sound too modest; sharpen it.}
\response We added an explicit ``What to cite this paper for'' statement to the
conclusion, naming the three publishable contributions: (i) a principled streaming form
of anchor regression with a fixed-anchor interventional-regret guarantee; (ii) an
interventional-robustness evaluation protocol; (iii) a diagnostic study, with a
pre-deployment checklist, for deciding when proactive anchor robustness is appropriate.

\reviewer{6. The Ader/AdaGrad mismatch remains a theoretical weakness; verify the claim
or do not make it.}
\response We took this seriously and \emph{tested} it rather than asserting it. We
implemented the Ader-wrapped variant (a five-expert step-size pool with a Hedge
meta-learner and projected OGD) and compared it with the deployed AdaGrad model on the
synthetic benchmark over 12 seeds (new Appendix~B). Both step rules deliver the
interventional-robustness benefit; their per-seed worst-case errors are rank-correlated
at Spearman $\rho=0.80$; and AdaGrad is in fact slightly more accurate and stable. The
theory/implementation remark now cites these measured numbers.

\reviewer{7. Visually separate the learned-channel method.}
\response \textsc{OARF-CD} is now labelled ``exploratory'' in the synthetic results
table and the baseline table, and is described throughout as an add-on rather than a
co-equal method.

\reviewer{8. Add a ``What to cite this paper for'' paragraph.}
\response Added to the conclusion (see point 5).

\reviewer{9. Box the practical recipe.}
\response The diagnostic recipe is now a boxed ``Pre-deployment checklist for OARF''
with the four checks (domain-valid anchor; stable anchor--residual correlation;
warm-up stress-test benefit; fallback if the channel is unstable), plus an explicit
gating/fallback rule.

\reviewer{10. More careful language around ``source of shifts.''}
\response We now describe the macro-financial series as an ``observable shift channel''
or co-moving proxy and reserve the strict causal reading for the synthetic SCM, where
it holds by construction.

\reviewer{11. The real-data event study is still absent.}
\response Added (new Appendix~C, with figure). We run fixed-anchor OARF and the OGD
floor around the COVID-19 crash and the 2022 energy shock, plotting the cumulative
squared-loss gap and the anchor--residual correlation. We report the result honestly:
OARF holds the anchor--residual correlation below OGD in \emph{every} window (the
mechanism is active), but leads on loss in only one of four window/commodity
combinations --- consistent with, and concretising, the null aggregate result rather
than demonstrating superiority.

\reviewer{12. Check appendix details for anonymity.}
\response The code repository is public and \emph{not} anonymised; we state this
explicitly and offer to provide an anonymised mirror and withhold the link until
acceptance should the journal require double-blind review.

\reviewer{13. Final proofreading; check accents, hats, arrows, line breaks.}
\response We diagnosed and fixed the underlying cause of the earlier
garbled-glyph rendering: the manuscript had been compiled with T1 font encoding without
the Latin~Modern / cm-super Type-1 fonts installed, which forced a bitmap Type-3
fallback for the body text. The text is now set in vector Computer Modern Type-1 fonts
(verified at the font level), and we re-checked mathematical accents, hats, arrows and
long-URL line breaks.

\section*{Earlier rounds}

For completeness, earlier revisions also: restructured the abstract into
problem/method/theory/evidence; rewrote the theorem as ``Fixed-anchor OARF
interventional regret'' with a complete proof; clarified Algorithm~1 (intercept vs
coefficient gradients, dimensions, ridge sign, projection); added stress tests and
assumption-violation scenarios mapping where the method fails; added warm-up
anchor-selector baselines; moved to 50-seed medians with interquartile ranges and an
alignment-versus-robustness scatter; and reframed the real-data section around the
Model Confidence Set with exact inclusion $p$-values.

\bigskip
We hope the reviewer finds the manuscript substantially strengthened and now suitable
for publication. We are grateful for the care that went into the reports and remain
happy to make further adjustments.

\bigskip
\noindent Sincerely,\\
The Authors

\end{document}
